### 2020-05-26 writeup/experiments.tex
sec 5

\textbf{Measuring data efficiency ratio.}
We measure the data efficiency ratio on text classification tasks.
We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.

\textbf{Data size affects covariance alignment.}
We validate that the performance of aligning task covariances depends on the size of source task data.
Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.

@@

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Averaged}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size.}
	\label{fig_covariate}
\end{figure}

>>>>

\textbf{Multi-task learning provides labeled data efficiency.}
We measure the data efficiency ratio on text classification tasks.
We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.

\textbf{Covariance alignment provides more improvement when data size is imbalanced.}
We validate that the performance of aligning task covariances depends on the size of source task data.
Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.

@@

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Averaged}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size. As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
	\label{fig_covariate}
\end{figure}
